Modelo de Simulac\'{i}on de circulaci\'{o}n Veh\'{i}culos\\ en las calles de San Jos\'{e}, Costa Rica

### 2013-05-06 Paper/main.tex
nuevas referencias

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  % \usepackage[nocompress]{cite}
\else
  % normal IEEE
  % \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
One of the most common problems in Costa Rica's capital, San Jose, is the heavy traffic jams we are usually exposed to. Any possible solutions is often applied and after a rate os success or failure, it is kept or discharched. It is mandatory to have a system available in the Ministery encharged of this issue a simulation model that envolves all the characteristics of the local situations. This paper shows how this simulations system is developed and the initial results of it.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

@@

% MAG SOLO CAMBIE EL NOMBRE DEL ARCHIVO...
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/FOTO-EDDY.JPG}}]{Mag Guevara-Rivera}
Biography text here.
\end{IEEEbiography}

>>>>

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
   \usepackage[nocompress]{cite}
\else
  % normal IEEE
   \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
One of the most common problems in Costa Rica's capital, San Jose, is the heavy traffic jams we are usually exposed to. Any possible solutions is often applied and after a rate os success or failure, it is kept or discharched. It is mandatory to have a system available in the Ministery encharged of this issue a simulation model that envolves all the characteristics of the local situations. This paper shows how this simulation system was developed according the particular needs that exist in Costa Rica and the initial results of it.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv, IEEEreferences}
\begin{thebibliography}{1}

\bibitem{HPerros}
H.Perros, \emph{Computer Simulation Techniques:
The definitive introduction!}, 2009. Computer Science Department. NC State University. Raleigh, NC. http://www4.ncsu.edu/~hp/simulation.pdf

\bibitem{SWeppner}
S.Weppner, \emph{Computational methods with depth and Flair}, September/October 2008. IEEE CS and the AIP. http://www2.computer.org/cms/Computer.org/
ComputingNow/bookreviews/archive/CiSE\%204.pdf

\bibitem{NDaneshjo}
N.Daneshjo, \emph{Computer Modeling and Simulation},2011. Sinaia, Romania.
http://www.ipcsit.com/vol8/12-S3.3.pdf

\bibitem{Villegas2012}
J. Villegas and L.Herrera, \emph{260.000 autos y 19.000 buses atascan San Jos\'{e} cada d\'{\i}a}, 2012, La Naci\'{o}n. San Jos\'{e}, Costa Rica. http://www.nacion.com/2012-03-17/ElPais/260-000-autos-y-19-000-buses-atascan-san-jose-cada-dia.aspx

\bibitem{Loaiza2007}
 V.Loaiza, \emph{Capital estrena sem\'{a}foros inteligentes en 180 intersecciones}, 2007. La Naci\'{o}n. San Jos\'{e}, Costa Rica. 
http://wvw.nacion.com/ln\_ee/2007/noviembre/28
/pais1332560.html

\bibitem{Mata2009}
A.Mata, \emph{Acceso libre a San Jos\'{e} provoca colapso vial}, 2009. La Naci\'{o}n. San Jos\'{e}, Costa Rica. 
http://wvw.nacion.com/ln\_ee/2009/junio/16/pais1997637.html

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/FOTO-MAG.JPG}}]{Mag Guevara-Rivera}
Mag naci\'o en 1991 en Managua, Nicaragua. Ingres\'o a la Universidad Nacional de Costa Rica donde se gradu\'o, en el 2011, como Bachiller en Ingenier\'ia de Sistemas de Informac\'ion y en el 2012 inici\'o sus estudios de Licenciatura en la misma Universidad. Actualmente, labora en una empresa de desarrollo de software para casas de apuestas y adicionalmente trabaja en conjunto con el COSEVI, y el MOPT en la realizaci\'on de un proyecto de investigaci\'on para poder usarse en sistemas de tr\'ansito. 
\end{IEEEbiography}
